Neural Power Unit \\-- A Bayesian Approach To Neural Arithmetic

### 2020-05-23 papers/main.tex
fuzz fuzz

\begin{figure}
  \centering
  \includegraphics[width=0.245\linewidth]{simple_err_add.pdf}
  \includegraphics[width=0.245\linewidth]{simple_err_mult.pdf}
  \includegraphics[width=0.245\linewidth]{simple_err_div.pdf}
  \includegraphics[width=0.245\linewidth]{simple_err_sqrt.pdf}
  \caption{Comparison of different models learning the function
  $(x,y)\rightarrow(xy,x/y)$ with $(x,y)\in\mathcal U^2(0.1,2)$.  Each
  plot shows the mean-squared error on a logarithmic color scale ($\hat{\bm
  t}=\text{model}(\bm x)$).  The Dense network learns both multiplication and
  division, but fails to extrapolate. NALU learns both tasks perfectly, but
  completely fails if one of the inputs is negative.  The NMU successfully
  learns multiplication, but not division. Only the NPU learns both tasks and
  can extrapolate with an error that is less than $0.01$ in most places.}%
  \label{fig:simple_err}
\end{figure}
\todo{add in depth experiment desc. of fig.~\ref{fig:simple_err} in appendix}
\begin{table}
  \centering
  \caption{Comparison of different $2\times2$ layers on the task
  $(x,y)\rightarrow(xy,\frac{x}{y})$.  $(x,y) \in \mathcal U^2(-2,2)$.}
  \label{tab:simple_err}
  \input{simple_err.tex}
\end{table}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.245\linewidth]{simple_err_add.pdf}
  \includegraphics[width=0.245\linewidth]{simple_err_mult.pdf}
  \includegraphics[width=0.245\linewidth]{simple_err_div.pdf}
  \includegraphics[width=0.245\linewidth]{simple_err_sqrt.pdf}
  \caption{Comparison of different models learning the function
  $(x,y)\rightarrow(x+y,xy,x/y,\sqrt(x))$ with $(x,y)\in\mathcal U^2(0.1,2)$.
  Each plot shows the mean-squared error on a logarithmic color scale
  ($\hat{\bm t}=\text{model}(\bm x)$) of the best model of 20 runs.
  The Dense network learns all tasks, but fails to extrapolate. NALU is
  slightly better at extrapolating to positive numbers, but fails if one of the
  inputs is negative.  The NMU successfully learns addition and multiplication,
  but not division and the square-root.  Only the NPU learns all tasks and can
  extrapolate both to positive and negative numbers.}%
  \label{fig:simple_err}
\end{figure}
\todo{add in depth experiment desc. of fig.~\ref{fig:simple_err} in appendix}
\begin{table}
  \centering
  \caption{Validation error of different models learning the function
  $(x,y)\rightarrow(x+y,xy,x/y,\sqrt(x))$ with $(x,y)\in\mathcal U^2(0.1,2)$.
  The validation ranges are $(x,y) \in -4.1:0.2:4$ for addition, multiplication,
  and division, and $(x,y) \in 0.1:0.2:4$ for the square-root.
  Each value is the averaged absolute of 20 models.
  }
  \label{tab:simple_err}
  \input{simple_err.tex}
\end{table}
